Language Bias in a Multilingual Tweet Corpus

### 2018-06-25 paper.tex
Minor

\footnotetext{In this paper, by \hl{``tracking users''}, we mean that their user IDs where passed to the Twitter API to collect tweets that they created, or the tweets that are replies by other users to their tweets. Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{to the Twitter documentation} for a complete description. Keep in mind that this is different from the case when a user follows another user.}

>>>>

\footnotetext{In this paper, by \hl{``tracking users''}, we mean that their user IDs where passed to the Twitter API to collect tweets that they created, retweets of those tweets, or the tweets that are replies by other users to their tweets. Refer to \href{https://developer.twitter.com/en/docs/tweets/filter-realtime/guides/basic-stream-parameters\#follow}{to the Twitter documentation} for a complete description. Keep in mind that this is different from the case when a user follows another user.}
